Consistency scores in text data

### 2020-07-23 outputs/documents/paper.Rmd
write-up on few-shot learning

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was released by OpenAI in June 2020 **(Ke-Li add ref)**. OpenAI is an AI research company who openly pursues Artificial General Intelligence—to have machines learn and understand any intellectual tasks as human do **(Ke-Li add ref)**. GPT-3 is the third Generative Pre-trained Transformer language model publicly released by OpenAI. It has '175 billion parameters' and can learn NLP tasks with just a few examples. OpenAI claims that the text generation by GPT-3 is 'difficult for humans to distinguish from authentic human content' **(Ke-Li add ref)**. Since the API of GPT-3 at the moment is only available to a few invited users, public applications of GPT-3 are limited. On the other hand, its predecessor, GPT-2, has enabled researchers made breakthroughs in the past years. Alt, Hubner and Henning extended GPT-2 to relation extraction, which is a task of identifying the relationship between concepts appeared in text. They had shown a milestone in predicting larger range of distinct relation types with higher confidence **(Ke-Li add ref)**. In the field of speech recognition, data scarcity is often an issue due to the difficulty to collect large amount of data from human for learning **(Ke-Li add ref)**. Bird, Faria, Ekart, Premebida and Ayrosa employed GPT-2 as part of the solution to generate augmented data for classification. GPT-2 also helped NLP researchers tackling the task of textual paraphrasing **(Ke-Li add ref)**. Hedge and Patil used GPT-2 to build an unsupervised paraphrasing model that is not restricted by domain shift within an article, which is a problem faced by the usual supervised models of paraphrasing.  
**(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**.

GPT is a Transformer-based model that has over 175 billions of parameters. **(Keli add citation)**. Proposed by Vaswani et al., the Transformer is a novel network architecture that outperforms RNN-based models in computational efficiency **(Keli add citation)**. The parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. In recent years, the growth of parameters of transformer language models expands rapidly which accelerate the improvements in text synthesis and downstream NLP tasks **(Keli add citation)**.

GPT-3 can learn NLP tasks with few examples and without any task-specific dataset **(Keli add citation)**. OpenAI refers this ability as few-shot learning. GPT-3 is pre-trained, and takes a sample of text as an input **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. 
**(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**

>>>>

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was announced by OpenAI in June 2020 **(Ke-Li add ref)**. OpenAI is an AI research company who openly pursues Artificial General Intelligence—to have machines learn and understand any intellectual tasks as human do **(Ke-Li add ref)**. GPT-3 is the third Generative Pre-trained Transformer language model publicly released by OpenAI. It has '175 billion parameters' and can learn NLP tasks with just a few examples. OpenAI claims that the text generation by GPT-3 is 'difficult for humans to distinguish from authentic human content' **(Ke-Li add ref)**. Since the API of GPT-3 at the moment is only available to a few invited users, public applications of GPT-3 are limited. On the other hand, its predecessor, GPT-2, has enabled researchers made breakthroughs in the past years. Alt, Hubner and Henning extended GPT-2 to relation extraction, which is a task of identifying the relationship between concepts appeared in text. They had shown a milestone in predicting larger range of distinct relation types with higher confidence **(Ke-Li add ref)**. In the field of speech recognition, data scarcity is often an issue due to the difficulty to collect large amount of data from human for learning **(Ke-Li add ref)**. Bird, Faria, Ekart, Premebida and Ayrosa employed GPT-2 as part of the solution to generate augmented data for classification. GPT-2 also helped NLP researchers tackling the task of textual paraphrasing **(Ke-Li add ref)**. Hedge and Patil used GPT-2 to build an unsupervised paraphrasing model that is not restricted by domain shift within an article, which is a problem faced by the usual supervised models of paraphrasing.  
**(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**.

GPT-3 is a Transformer-based model that has over 175 billions of parameters. **(Keli add citation)**. Proposed by Vaswani et al., the Transformer is a novel network architecture that outperforms RNN-based models in computational efficiency **(Keli add citation)**. The parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. In the past few years, the growth of parameters of transformer language models expands rapidly. The first generation GPT has 110 million parameters. Released in 2018, GPT-2 has 1.6 billion parameters, and within two years, GPT-3 has grown the size to 175 billion, which is over 100 times than its predecessor . The more parameters there are the better the model can generalize to new tasks; therefore, the increasing amount of parameters accelerates the improvements in text synthesis and downstream NLP tasks **(Keli add citation)**. GPT-3 can learn NLP tasks with just a handful of example; OpenAI refers this ability as few-shot learning, or in-context learning. Few-shot learning means that the model  **(Keli add citation)**. 
As a result, we only need to provide GPT-3 a few demonstrations for it to learn a new NLP task. **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. For example, OpenAI team trained GPT-3 to generate "news articles". The prompt input is a plausible first sentence of a news story written by human, and the output is an entire news article generated by the model itself. Without the demonstrations, GPT-3 tends to treat the prompts as "tweets" and generate texts that serve as responses or follow-up tweets. The team fed a few previous news articles in the model’s context as demonstrations, and the model learned to produce the outputs that adapt to the style and length of news stories **(Keli add citation)**. This few-shot learning ability indicates that the model can learn like human do and would democratize the use of language models to broader fields. **(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**
